---
title: "STAT/MATH 495: Problem Set 04"
author: "WRITE YOUR NAME HERE"
date: "2017-10-03"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 2
    collapsed: false
    smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width=8, fig.height=4.5, message=FALSE)
library(tidyverse)
library(caret)
library(caTools)
library(mosaic)
library(dplyr)
set.seed(76)
```

# Collaboration

Please indicate who you collaborated with on this assignment: Jeff L.


# Load packages, data, model formulas

```{r, warning=FALSE}

library(tidyverse)
credit <- read_csv("http://www-bcf.usc.edu/~gareth/ISL/Credit.csv") %>%
  select(-X1) %>%
  mutate(ID = 1:n()) %>% 
  select(ID, Balance, Income, Limit, Rating, Age, Cards, Education)
```

You will train the following 7 models on `credit_train`...

... where `credit_train` is defined below, along with `credit_test`.

```{r}
set.seed(79)
credit_train <- credit %>% 
  sample_n(20)
credit_test <- credit %>% 
  anti_join(credit_train, by="ID")
```


Training models on `credit_train`
```{r}
model1_formula <- as.formula("Balance ~ 1")

model_1 <- lm(model1_formula, data=credit_train)

model_1 %>% 
  broom::tidy(conf.int=TRUE)

model2_formula <- as.formula("Balance ~ Income")

model_2 <- lm(model2_formula, data=credit_train)

model_2 %>% 
  broom::tidy(conf.int=TRUE)


model3_formula <- as.formula("Balance ~ Income + Limit")

model_3 <- lm(model3_formula, data=credit_train)

model_3 %>% # Good P-values for coefficients
  broom::tidy(conf.int=TRUE)


model4_formula <- as.formula("Balance ~ Income + Limit + Rating")

model_4 <- lm(model4_formula, data=credit_train)

model_4 %>% 
  broom::tidy(conf.int=TRUE)


model5_formula <- as.formula("Balance ~ Income + Limit + Rating + Age")

model_5 <- lm(model5_formula, data=credit_train)

model_5 %>% 
  broom::tidy(conf.int=TRUE)

model6_formula <- as.formula("Balance ~ Income + Limit + Rating + Age + Cards")

model_6 <- lm(model6_formula, data=credit_train)

model_6 %>% 
  broom::tidy(conf.int=TRUE)


model7_formula <- as.formula("Balance ~ Income + Limit + Rating + Age + Cards + Education")

model_7 <- lm(model7_formula, data=credit_train)

model_7 %>% 
  broom::tidy(conf.int=TRUE)
```


Make Predictions on Test Data
```{r}
set.seed(10)

Predict1 <- model_1 %>% 
  broom::augment(data=credit_test)

Summary1 <- summary(Predict1)

ggplot(NULL) +
  geom_point(data=Predict1, aes(x=1, y=Balance)) +
  geom_line(data=Predict1, aes(x=1, y=Balance), col="blue") +
  geom_point(data=Predict1, aes(x=1, y=Balance), col="red") +
  labs(x="1", y="Balance")

Predict2 <- model_2 %>% 
  broom::augment(data=credit_test)

Summary2 <- summary(Predict2)

ggplot(NULL) +
  geom_point(data=Predict2, aes(x=Income, y=Balance)) +
  geom_line(data=Predict2, aes(x=Income, y=Balance), col="blue") +
  geom_point(data=Predict2, aes(x=Income, y=Balance), col="red") +
  labs(x="Income", y="Balance")

Predict3 <- model_3 %>% 
  broom::augment(data=credit_test)

Summary3 <- summary(Predict3)

ggplot(NULL) +
  geom_point(data=Predict3, aes(x=Income + Limit, y=Balance)) +
  geom_line(data=Predict3, aes(x=Income + Limit, y=Balance), col="blue") +
  geom_point(data=Predict3, aes(x=Income + Limit, y=Balance), col="red") +
  labs(x="Income + Limit", y="Balance")

Predict4 <- model_4 %>% 
  broom::augment(data=credit_test)

Summary4 <- summary(Predict4)

ggplot(NULL) +
  geom_point(data=Predict4, aes(x=Income + Limit + Rating, y=Balance)) +
  geom_line(data=Predict4, aes(x=Income + Limit + Rating, y=Balance), col="blue") +
  geom_point(data=Predict4, aes(x=Income + Limit + Rating, y=Balance), col="red") +
  labs(x="Income + Limit + Rating", y="Balance")

Predict5 <- model_5 %>% 
  broom::augment(data=credit_test)

Summary5 <- summary(Predict5)

ggplot(NULL) +
  geom_point(data=Predict5, aes(x=Income + Limit + Rating + Age, y=Balance)) +
  geom_line(data=Predict5, aes(x=Income + Limit + Rating + Age, y=Balance), col="blue") +
  geom_point(data=Predict5, aes(x=Income + Limit + Rating + Age, y=Balance), col="red") +
  labs(x="Income + Limit + Rating + Age", y="Balance")

Predict6 <- model_6 %>% 
  broom::augment(data=credit_test)

Summary6 <- summary(Predict6)

ggplot(NULL) +
  geom_point(data=Predict6, aes(x=Income + Limit + Rating + Age + Cards, y=Balance)) +
  geom_line(data=Predict6, aes(x=Income + Limit + Rating + Age + Cards, y=Balance), col="blue") +
  geom_point(data=Predict6, aes(x=Income + Limit + Rating + Age + Cards, y=Balance), col="red") +
  labs(x="Income + Limit + Rating + Age + Cards", y="Balance")


Predict7 <- model_7 %>% 
  broom::augment(data=credit_test)

Summary7 <- summary(Predict7)

ggplot(NULL) +
  geom_point(data=Predict6, aes(x=Income + Limit + Rating + Age + Cards + Education, y=Balance)) +
  geom_line(data=Predict6, aes(x=Income + Limit + Rating + Age + Cards + Education, y=Balance), col="blue") +
  geom_point(data=Predict6, aes(x=Income + Limit + Rating + Age + Cards + Education, y=Balance), col="red") +
  labs(x="Income + Limit + Rating + Age + Cards + Education", y="Balance")

```



# RMSE vs number of coefficients

```{r, echo=TRUE, warning=FALSE, message=FALSE}
# Placeholder vectors of length 7. For now, I've filled them with arbitrary 
# values; you will fill these in
RMSE_train <- runif(n=7)
RMSE_test <- runif(n=7)


# Do your work here:

# Save results in a data frame. Note this data frame is in wide format.
results <- data_frame(
  num_coefficients = 1:7,
  RMSE_train,
  RMSE_test
) 

# Some cleaning of results
results <- results %>% 
  # More intuitive names:
  rename(
    `Training data` = RMSE_train,
    `Test data` = RMSE_test
  ) %>% 
  # Convert results data frame to "tidy" data format i.e. long format, so that we
  # can ggplot it
  gather(type, RMSE, -num_coefficients)

ggplot(results, aes(x=num_coefficients, y=RMSE, col=type)) +
  geom_line() + 
  labs(x="# of coefficients", y="RMSE", col="Data used to evaluate \nperformance of fitted model")
```


# Interpret the graph

Compare and contrast the two curves and hypothesize as to the root cause of any differences.

Didn't finish.

# Bonus

Repeat the whole process, but let `credit_train` be a random sample of size 380
from `credit` instead of 20. Now compare and contrast this graph with the
one above and hypothesize as to the root cause of any differences.

```{r, echo=FALSE}

```
